---
title: "Results"
author: "Joel larwood"
date: "2020-07-24"
output: workflowr::wflow_html
editor_options:
  chunk_output_type: console
---

## Introduction

```{r}
library(tidyverse)
library(emmeans)
```


It is expected that alexithymia will moderate the relationship between affective category and affect ratings. Specifically we predicted that people high in alexithymia would make more neutral judgements of valence and arousal when the target valence of the song was negative. 

We pre-registered a hypothesis that included only affective category and alexithymia. We have additionally provided alternative models that allowed for depression and song liking to be entered as control variables. 

Here I am following up models that have been pre-fit. 

# Self reported valence

```{r loadvalence}

valence_models<- list.files(path = here::here("analysis", "models", "valence"), full.names = T)

```

## Factor only Model

In this model we can see that there is no difference in ratings for valence within valence category 
```{r}
print(valence_models[5])
valence_factor <- read_rds(valence_models[5])
afex::nice(valence_factor)

pairs(emmeans::emmeans(valence_factor, specs = "factor"))
emmeans::emmip(valence_factor, ~factor, plotit = FALSE) %>% 
  ggplot2::ggplot(aes(x = xvar,
                      y = yvar)) +
  ggplot2::geom_point() +
  ggplot2::geom_errorbar(aes(
    ymin = yvar - SE,
    ymax = yvar + SE,
    width = .2
  )) +
  geom_hline(yintercept = 3, linetype = "dashed") +
  ggplot2::ylim(1,5) +
  theme_classic()+
  ylab("Valence Rating") + 
  xlab("Affective Category")

```

## Alexithymia x Factor Interaction 

Her we can see there is no interaction with anelxithymia
```{r}
print(valence_models[4])
valence_factor_tas <- read_rds(valence_models[4])
afex::nice(valence_factor_tas)

pairs(emtrends(valence_factor_tas, ~ factor, var = "tas_z"))

```


print(valence_models[1])
valence_factor_liking_tas_dep <- read_rds(valence_models[1])
afex::nice(valence_factor_liking_tas_dep)


print(valence_models[2])
valence_factor_liking_tas <- read_rds(valence_models[2])

print(valence_models[3])
valence_factor_liking <- read_rds(valence_models[3])




# Arousal Ratings 

```{r}
arousal_models <- list.files(path = here::here("analysis", "models", "arousal"), full.names = T)
```

## Alexithymia x Factor Interaction 

Her we can see there is no interaction with anelxithymia
```{r}
print(arousal_models[4])
arousal_factor_tas <- read_rds(arousal_models[4])
afex::nice(arousal_factor_tas)

pairs(emtrends(arousal_factor_tas, ~ factor, var = "tas_z"))

```





```{r}
psychopy <- here::here(
  "data",
  "psychopy_long.csv"
) %>% 
  read_csv() %>% 
  mutate(
    id = as.factor(str_remove(participant, "^0+")),
    song = as.factor(songmark),
    factor = fct_relevel(
      affect_label, 
      "Positive/Low",
      "Positive/High",
      "Negative/Low",
      "Negative/High"
    )
  )

glimpse(psychopy)

survey <- here::here(
  "data",
  "survey_responses.csv"
) %>% 
  read_csv() %>% 
  mutate(
    id = as.factor(id),
    tas_c = tas - mean(tas),
    dep_c = depression - mean(depression)
  )

## Physiology data 


data <- psychopy %>% 
  left_join(survey, 
            by = "id")

```

# Analysis of self-report 

```{r}
self_report_analyse <- data %>% 
    select(
    id,
    song,
    factor,
    arousal_rating,
    valence_rating,
    liking_c,
    tas_c,
    dep_c
  ) 

glimpse(sample_n(self_report_analyse, 20))
```

## Hypothesised models 

The hypothesised models included only the fixed effects of the affective category, alexithymia, and their interaction. 

### Valence
Here we can see that there is no statstically significant interaction with alexithymia

```{r}
hyp_valence <- afex::mixed(
  valence_rating ~ factor * tas_c + (1 + factor | id) + (1|song),
  data = self_report_analyse
)

afex::nice(hyp_valence)
```

We can also see that valence was rated higher for songs which had a nomially positive valence. Further we can see valence was equatable among nominaly negative songs and aong nomially positive songs

```{r}
pairs(emmeans::emmeans(hyp_valence, ~factor))
```


### Arousal 

Here we can see that there is no statstically significant interaction with alexithymia

```{r}
hyp_arousal <- afex::mixed(
  arousal_rating ~ factor * tas_c + (1 + factor | id) + (1|song),
  data = self_report_analyse
)

afex::nice(hyp_arousal)
```

We can also see that arousal was rated higher for songs which were nomially high in arousal. However, we can also see that arousal was not equitable among positive songs that were both nimally low in arousal, with a similar trend emerging for that were nomially high in arousal

```{r}
pairs(emmeans::emmeans(hyp_arousal, ~factor))
```


### Follow up model with liking included 

```{r}
liking_valence <- afex::mixed(
  valence_rating ~ factor * tas_c * liking_c + (1 + factor | id) + (1|song),
  data = self_report_analyse
)

afex::nice(liking_valence)


```

#### Follow up tests
```{r}




```


```{r}
self_report_analyse <- here::here(
  "data",
  "self_report_only.csv"
) %>% 
  read_csv() %>% 


```


```{r echo=TRUE}
self_report_analyse <- self_report_analyse %>% 
  mutate(
    tas_c = tas - mean(tas, na.rm = TRUE),
    dep_c = depression -mean(depression, na.rm = TRUE),
    liking_c = liking - mean(liking, na.rm = TRUE)
  )

self_report_analyse %>% 
  select(id, 
         contains("_c"),
         -liking_c
         ) %>% 
  pivot_longer(
    cols = -id, 
    names_to = "measure",
    values_to = "value"
  ) %>% 
  mutate(measure = factor(measure))%>% 
  distinct(id, measure, value)%>% 
  ggplot(aes(x = value,
             fill = measure)) + 
  geom_histogram(aes(y = ..density..)) + 
  geom_density(alpha = .2) +
  facet_wrap(~measure) + 
  theme(legend.position = "none") +
  theme_classic()

```


# Valence ratings 

From the models below it can be seen that the best fitting model, which includes, alexithymia, was the model that included liking of the song. 

```{r}
v_hyp_model <- lmerTest::lmer(
  formula = valence_rating ~ factor*tas_c + (1 + factor|id) + (1 | songmark),
  data = self_report_analyse)

v_like_control <- lmerTest::lmer(
  formula = valence_rating ~ factor*tas_c + factor*liking_c + (1 + factor|id) + (1 | songmark),
  data = self_report_analyse)

v_dep_control <- lmerTest::lmer(
  formula = valence_rating ~ factor*tas_c + factor*dep_c + (1 + factor|id) + (1 | songmark),
  data = self_report_analyse)

v_all_control <- lmerTest::lmer(
  formula = valence_rating ~ factor*tas_c + factor*dep_c + factor*liking_c + (1 + factor|id) + (1 | songmark),
  data = self_report_analyse)

sjPlot::tab_model(
  v_hyp_model,
  v_like_control,
  v_dep_control,
  v_all_control,
  show.est = FALSE,
  show.std = TRUE,
  show.aic = TRUE
)

```

## Simple Slopes
```{r}

interactions::sim_slopes(
  model = v_like_control, 
  pred = tas_c,
  modx = factor
)

interactions::interact_plot(
  model = v_like_control, 
  pred = tas_c,
  modx = factor,
  interval = TRUE
) + 
  ylim(1,5) +
  theme_classic()
```

# Arousal Model

From the models below it can be seen that the best fitting model, which includes, alexithymia, was the model that included liking of the song. 

```{r}

a_hyp_model <- lmerTest::lmer(
  formula = arousal_rating ~ factor*tas_c + (1 + factor|id) + (1 | songmark),
  data = self_report_analyse)

a_like_control <- lmerTest::lmer(
  formula = arousal_rating ~ factor*tas_c + factor*liking_c + (1 + factor|id) + (1 | songmark),
  data = self_report_analyse)

a_dep_control <- lmerTest::lmer(
  formula = arousal_rating ~ factor*tas_c + factor*dep_c + (1 + factor|id) + (1 | songmark),
  data = self_report_analyse)

a_all_control <- lmerTest::lmer(
  formula = arousal_rating ~ factor*tas_c + factor*dep_c + factor*liking_c + (1 + factor|id) + (1 | songmark),
  data = self_report_analyse)

sjPlot::tab_model(
  a_hyp_model,
  a_like_control,
  a_dep_control,
  a_all_control,
  show.est = FALSE,
  show.std = TRUE,
  show.aic = TRUE
)

```

## Simple Slopes

The simple slopes additionally reveal that high alexithymia was related to lower arousal ratings when the arousal was high and the valence negative
```{r}

interactions::sim_slopes(
  model = a_like_control, 
  pred = tas_c,
  modx = factor
)

interactions::interact_plot(
  model = a_like_control, 
  pred = tas_c,
  modx = factor,
  interval = TRUE
) + 
  ylim(1,5) +
  theme_classic()
```

# Exploratory analysis of target emotion ratings 

The orignal stimulus set found the 2D valence model to better fit the data than descrete emotion labels. However we also collected ratings of the target emotions of the songs. 

Below I recode the affective category into target emotions with the following correspondence
- Positive Valence / Low Arousal = Tender
- Positive Valence / High Arousal = Happy
- Negative Valence / Low Arousal = Sad 
- Negative Valence / High Arousal = Fear 


```{r}
target_data <- self_report_analyse %>% 
  mutate(
    target_emotion = as.factor(
      recode(
        factor, 
        "Positive/High" = "happy",
        "Negative/High" = "fear",
        "Negative/Low" = "sad",
        "Positive/Low" = "tender")),
    target_rating = if_else(
      target_emotion == "fear", 
      scared, 
      if_else(
        target_emotion == "sad", 
        sad, 
        if_else(
          target_emotion == "tender", 
          tender, 
          happy)
      )
    )
  ) 

```

The descriptives for each can be seen here 

```{r}

means <- target_data %>% 
  group_by(target_emotion) %>% 
  summarise(mean = mean(target_rating))

target_data %>% 
  ggplot(
    aes(x = target_rating,
        color = target_emotion,
        fill = target_emotion)
    ) +
  geom_histogram(alpha = .5,
                 bins = 5,
                 binwidth = 1) + 
  geom_vline(data = means, 
             aes(xintercept = mean),
             linetype = "dashed") + 
  facet_wrap(~target_emotion) + 
  theme(legend.position = 'none') + 
  theme_classic() +
  coord_flip()
```

## Predicting Target Emotion Rating with alexithymia 

We can again see the best fitting model is the model that included liking along with alexithymia

```{r}
emotion_tas_model <- lmerTest::lmer(
  formula = target_rating ~ target_emotion*tas_c + (1 + target_emotion|id) + (1 | songmark),
  data = target_data)

emotion_like_control <- lmerTest::lmer(
  formula = target_rating ~ target_emotion*tas_c + target_emotion*liking_c + (1 + target_emotion|id) + (1 | songmark),
  data = target_data)

emotion_dep_control <- lmerTest::lmer(
  formula = target_rating ~ target_emotion*tas_c + target_emotion*dep_c + (1 + target_emotion|id) + (1 | songmark),
  data = target_data)

emotion_all_control <- lmerTest::lmer(
  formula = target_rating ~ target_emotion*tas_c + target_emotion*dep_c + target_emotion*liking_c + (1 + target_emotion|id) + (1 | songmark),
  data = target_data)

sjPlot::tab_model(
  emotion_tas_model,
  emotion_like_control,
  emotion_dep_control,
  emotion_all_control,
  show.est = FALSE,
  show.std = TRUE,
  show.aic = TRUE
)

```

## Simple Slopes

The simple slopes additionally reveal that high alexithymia was related to lower arousal ratings when the arousal was high and the valence negative.

From the slopes we can see that alexithymia only influenced that ratings of tender songs. 
```{r}

interactions::sim_slopes(
  model = emotion_like_control, 
  pred = tas_c,
  modx = target_emotion
)

interactions::interact_plot(
  model = emotion_like_control, 
  pred = tas_c,
  modx = target_emotion,
  interval = TRUE
) + 
  ylim(1,5) +
  theme_classic()
```
